---
title: "Validate Central Limit Theorem using Simulation"
author: "Zhao Zheng"
date: "8/17/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What is Central Limit Theorem?

- If you have a population with mean $\mu$ and standard deviation $\sigma$ and take sufficiently large random samples (with sample size n) from the population with replacement, then the distribution of the **sample means** will be approximately normally distributed, with mean $\mu$ and standard deviation $\sigma/\sqrt{n}$. 

- For more details on Central Limit Theorem, please referring to the Wikipedia link below:
<https://en.wikipedia.org/wiki/Central_limit_theorem>


## Introduction to my Shiny App
- In my Shiny Application "Validate Central Limit Theorem using Simulation", users will be able to see how does the CLT work.  
<https://zhaozheng.shinyapps.io/testing_clt/>

- No matter which distribution the users choose to start with, the simulated sample means will be normally distributed. 

- The effect will be more obvious with large number of simulation (even with a small sample size).

- Please refer to the link below to my Github Repo, which includes all the coding files to my Shiny app and this presentation.  
<https://github.com/ZhaoZ-2020/DevelopDataProducts>


## Input and Output to my Shiny App

##### Users can choose the original distribution (where the sample will be drawn) from the four distributions below:
  
    - Standard Normal Distribution 
    - Poisson Distribution (with lambda = 1)
    - Standard Uniform Distribution
    - Binomial Distribution (with n=10 and p=0.5)

##### Users will need to specifiy the sample size and the number of simulation they want to perform using the sliders provided.  
  
##### In addition, they can also indicate if they want to show the extra lines below in the output plots:
  
    - sample mean in the first density plot
    - average of the sample mean in the second density plot
    - density plot from a normal distribution (for comparison purpose)
      

## Output from my Shiny App

See example below from standard Uniform distribution with n=5 and B=1000:

```{r, echo=TRUE, fig.height=3}
set.seed(123); par(mfrow=c(1,2)); n<-5; B<-1000
x<-matrix(runif(n*B),nrow=B); xbar<-apply(x,1,mean)
hist(x[1,],prob=TRUE,main="Density plot of one sample")
hist(xbar,col='lightblue',prob=TRUE,main="Density plot of B sample means")
```





